Transparency in Science

### 2023-05-20 presentation.Rmd
reorder slides

---
background-image: url("images/contribution.svg")
background-position: center
background-size: contain

@@

@@

@@

$\mathcal{L}(\text{Theory}, \text{Data})$ is just an estimate.

@@

@@

@@

# Bias

@@

.large.transparent[Under some circumstances,]

@@

.large[is the ability of a model to accommodate random data.]

@@

.large[Under some circumstances,]

@@

.large[can be approximated.]

.large[ .highlight[Reproducibility] is a necessary condition to estimate:]

.huge[
$\mathcal{C}(\text{Model})$]

.transparent[*In an ideal world.]

@@

$$\mathcal{C}(\text{Statistical Model})$$

@@

.small.right.grey[*In an ideal world.]
---
background-image: url("images/contribution1.svg")
background-position: center
background-size: contain
---
background-image: url("images/contribution2.svg")
background-position: center
background-size: contain
---
background-image: url("images/contribution3.svg")
background-position: center
background-size: contain
---
background-image: url("images/contribution4.svg")
background-position: center
background-size: contain
---
class: middle

>>>>

---
background-image: url("images/contribution_path.svg")
background-position: center
background-size: contain

@@

$\mathcal{L}(\text{Theory}, \text{Reality})$

@@

.transparent[is just an estimate.]

@@

@@

is just an estimate.

@@

##.right.red[precision]

##.right.red[predictions]

@@

#.red[Bias]

@@

@@

@@

@@

@@

@@

$$\mathcal{C}(\text{Model})$$

---
background-image: url("images/contribution1_path.svg")
background-position: center
background-size: contain
---
background-image: url("images/contribution2_path.svg")
background-position: center
background-size: contain
---
background-image: url("images/contribution3_path.svg")
background-position: center
background-size: contain
---
background-image: url("images/contribution4_path.svg")
background-position: center
background-size: contain
---
class: middle
